Partitioned Local Depth (PaLD) Community Analyses in R

### 2023-09-28 2023-r-journal/dagostino-mcgowan.tex
update fig

\begin{Schunk}
\begin{Sinput}
graphs <- community_graphs(cohesion)
graphs[["G_strong"]]
\end{Sinput}
\begin{Soutput}
#> IGRAPH 198a54e UNW- 6 3 -- 
#> + attr: name (v/c), weight (e/n)
#> + edges from 198a54e (vertex names):
#> [1] A--B A--E D--F
\end{Soutput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
french_neighbors <- igraph::neighbors(cognate_graph_strong, "French")
french_neighbors
\end{Sinput}
\begin{Soutput}
#> + 8/87 vertices, named, from dc83183:
#> [1] Italian         Ladin           Provencal       Walloon        
#> [5] French_Creole_C French_Creole_D Spanish         Catalan
\end{Soutput}
\end{Schunk}

@@

exdata_pald <- community_clusters(exdata_cohesion)$cluster

>>>>

\begin{Schunk}
\begin{Sinput}
graphs <- community_graphs(cohesion)
graphs[["G_strong"]]
\end{Sinput}
\begin{Soutput}
#> IGRAPH 90d60fd UNW- 6 3 -- 
#> + attr: name (v/c), weight (e/n)
#> + edges from 90d60fd (vertex names):
#> [1] A--B A--E D--F
\end{Soutput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
french_neighbors <- igraph::neighbors(cognate_graph_strong, "French")
french_neighbors
\end{Sinput}
\begin{Soutput}
#> + 8/87 vertices, named, from aab3808:
#> [1] Italian         Ladin           Provencal       Walloon        
#> [5] French_Creole_C French_Creole_D Spanish         Catalan
\end{Soutput}
\end{Schunk}

@@

exdata_pald <- community_clusters(exdata_cohesion)$community
